\vskip-0.6in Temporary Trade Barriers: When Will They End?

### 2017-09-19 draft.tex
revise start of sec:pref; change ML to G throughout

\subsection{Preferences}
\label{sec:pref}
With the structure of politics and the economy symmetric and the latter fully separable, I focus on the home country's and the $X$-sector. The details are analogous for $Y$ and foreign. The home legislature's welfare function is
\begin{equation}
  W_{\mathit{ML}} = \mathit{CS}_X(\tau) + \ga(e,\ve) \cdot \pi_X(\tau) + \mathit{CS}_Y(\tau^*) + \pi_Y(\tau^*) + \mathit{TR}(\tau)
  \label{eq:ml}
\end{equation}
where $\mathit{CS}$ is consumer surplus, $\pi$ are profits, $\ga(e,\ta)$ is the weight placed on profits in the import-competing industry, and $\mathit{TR}$ is tariff revenue.\footnote{Labor income $l$ could also be included in both median legislator and executive welfare. I omit it because its inclusion alters none of the results and only serves to complicate the exposition.} I model the decisions of the legislature as being taken by a median legislator with the weight the median legislator places on import-competing industry profits affected by the level of lobbying effort $e$ and a random variable $\ta$. I make the following assumptions on $\ga(e,\ta)$:

@@

\bigskip
\subsection{To Break or Not to Break?}
\label{sec:break}
We can now proceed by backward induction to analyze the legislature's incentives to uphold or break the trade agreement. The legislature will break the agreement and set the tariff at $\tau^n$ if the median legislator's utility from the Nash tariffs is higher than his utility from the trade agreement tariffs, i.e. if
\begin{equation}
  W_{ML}(\btn,\ga(e_b,\ve_b)) > W_{ML}\left(\bta,\ga(e_b,\ve_b)\right)
  \label{eq:lwcg}
\end{equation}

The outcome of the vote on whether or not to break the trade agreement is not known to \textit{any} player until the uncertainty over the identity of the median legislator is resolved at the moment the vote takes place. I represent the probability that the home legislature breaks the trade agreement and sets the tariff at $\tau^n$ as:\footnote{I suppress the Nash tariffs in the expression of the break probability since they do not vary from the point of view of earlier stages.}
\begin{multline}
  b(e_b,\bta) = \expect_{\ga|e_b} \bm{1} [ W_{ML}(\btn,\ga(e_b,\ve_b)) > W_{ML}\left(\bta,\ga(e_b,\ve_b)\right) ] \\ = \Pr [ W_{ML}(\btn,\ga(e_b,\ve_b)) > W_{ML}\left(\bta,\ga(e_b,\ve_b)\right) | e_b]
  \label{eq:b}
\end{multline}

>>>>

\subsection{Preferences}
\label{sec:pref}
With foreign not active in setting policy and the structure the economy symmetric and fully separable, I focus on the home country and the $X$-sector, which is the only politically active sector. The government agency's welfare is given by
\begin{equation}
  W_{\mathit{G}} = \mathit{CS}_X(\tau) + \ga(e,\ve) \cdot \pi_X(\tau) + \mathit{CS}_Y(\tau^*) + \pi_Y(\tau^*) + \mathit{TR}(\tau)
  \label{eq:ml}
\end{equation}
where $\mathit{CS}$ is consumer surplus, $\pi$ are profits, $\ga(e,\ta)$ is the weight placed on profits in the import-competing industry, and $\mathit{TR}$ is tariff revenue.\footnote{Labor income $l$ could also be included in both median legislator and executive welfare. I omit it because its inclusion alters none of the results and only serves to complicate the exposition.} I model the decisions of the legislature as being taken by a median legislator with the weight the median legislator places on import-competing industry profits affected by the level of lobbying effort $e$ and a random variable $\ta$. I make the following assumptions on $\ga(e,\ta)$:

@@

\bigskip
\subsection{To Break or Not to Break?}
\label{sec:break}
We can now proceed by backward induction to analyze the legislature's incentives to uphold or break the trade agreement. The legislature will break the agreement and set the tariff at $\tau^n$ if the median legislator's utility from the Nash tariffs is higher than his utility from the trade agreement tariffs, i.e. if
\begin{equation}
  W_G(\btn,\ga(e_b,\ve_b)) > W_G\left(\bta,\ga(e_b,\ve_b)\right)
  \label{eq:lwcg}
\end{equation}

The outcome of the vote on whether or not to break the trade agreement is not known to \textit{any} player until the uncertainty over the identity of the median legislator is resolved at the moment the vote takes place. I represent the probability that the home legislature breaks the trade agreement and sets the tariff at $\tau^n$ as:\footnote{I suppress the Nash tariffs in the expression of the break probability since they do not vary from the point of view of earlier stages.}
\begin{multline}
  b(e_b,\bta) = \expect_{\ga|e_b} \bm{1} [ W_G(\btn,\ga(e_b,\ve_b)) > W_G\left(\bta,\ga(e_b,\ve_b)\right) ] \\ = \Pr [ W_G(\btn,\ga(e_b,\ve_b)) > W_G\left(\bta,\ga(e_b,\ve_b)\right) | e_b]
  \label{eq:b}
\end{multline}
